% Resume based on MIT-licensed template by Jake Gutierrez
\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Sauraj Kumar Singh} \\ \vspace{1pt}
    Noida, India \quad $|$ \quad +91-8986328898 \quad $|$ \href{mailto:ksauraj1@gmail.com}{ksauraj1@gmail.com} \\
    \href{https://linkedin.com/in/sauraj-kumar-singh-807295226}{linkedin.com/in/sauraj-kumar-singh} \quad $|$ 
    \href{https://github.com/ksauraj}{github.com/ksauraj} \quad $|$ 
    \href{https://ksauraj.eu.org}{ksauraj.eu.org}


\end{center}

    \vspace{4pt}
\small{\textbf{MBTI: INTP} --- Introverted, Intuitive, Thinking, Perceiving}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern - DevOps}{May 2025 -- Present}
      {ES Magico AI Studio}{Remote}
      \resumeItemListStart
        \resumeItem{Led deployment setup across multiple projects using Docker and GitHub Actions.}
        \resumeItem{Set up scalable monitoring and load balancing with multi-instance support inside custom VPCs.}
        \resumeItem{Migrated DNS infrastructure from Route 53 to Cloudflare and integrated Kong API Gateway for multiple projects.}
        \resumeItem{Integrated a comprehensive security pipeline into the main DevOps workflow, automating threat detection, password strength validation, and DDoS monitoring using custom scripts and tools.}
        \resumeItem{Automated provisioning and infrastructure using Terraform, Ansible, and Make-based workflows.}
        \resumeItem{Designed and implemented Azure infrastructure including Virtual Networks (VNet), Application Gateway, and Virtual Machine Scale Sets (VMSS) for high availability and controlled traffic routing.}
        \resumeItem{Built and managed AWS infrastructure with VPC design, Application Load Balancers (ALB), and Auto Scaling Groups to support horizontally scalable services.}
        \resumeItem{Developed custom scripts to manage and inject environment variables securely using HashiCorp Vault across multiple environments.}
        \resumeItem{Performed load and stress testing on production-like environments to validate scalability, fault tolerance, and traffic handling limits.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Backend Developer Intern}{Feb 2025 -- June 2025}
      {Welmun-Tech India Pvt Ltd}{Remote}
      \resumeItemListStart
        \resumeItem{Contributed to DevOps practices including CI/CD pipelines, containerization using Docker, and basic Kubernetes orchestration.}
        \resumeItem{Assisted in architecting microservices and applying event-driven design patterns for modular services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------OPEN SOURCE-----------
\section{Open Source Contributions}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Maintainer}{2021 -- 2022}
      {}{}
      {\textbf{CipherOS} \href{https://cipheros.online}{\textbar{} cipheros.online}} \\
      \resumeItemListStart
        \resumeItem{Maintained device tree for RMX2151 and handled CI/CD workflows to automate Android build releases.}
        \resumeItem{Managed project automation via GitHub Actions and optimized pipeline performance and debugging.}
      \resumeItemListEnd

      \vspace{4pt}
      {\textbf{PixelPlusUI} \href{https://ppui.site/}{\textbar{} ppui.site} \href{https://xdaforums.com/t/rom-official-11-0-rmx2151-pixelplus-ui-3-9-aosp-2021-09-12.4283233/}{\textbar{} XDA Thread}} \\
      \resumeItemListStart
        \resumeItem{Maintained Android ROM builds for RMX2151 and provided timely OTA updates to the community.}
        \resumeItem{Authored utility scripts to streamline test builds and automated file uploads for CI-based workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{ksau CLI/Web Tool} \emph{(Go, Bash)} \href{https://github.com/global-index-source/ksau-go}{[GitHub]}}{2021 - 2025}
      \resumeItemListStart
        \resumeItem{Designed a CLI and web tool for file uploads to OneDrive using Microsoft Graph API.}
        \resumeItem{Migrated from Bash to Golang for better concurrency, performance, and maintainability.}
        \resumeItem{Developed the backend API, which is used in the ksau-py, and designed the web version.}
        \resumeItem{Deployed link: \href{https://ksau.ksauraj.eu.org}{ksau.ksauraj.eu.org}.}
      \resumeItemListEnd


    \resumeProjectHeading
      {\textbf{JEE Counsellor} \emph{(Python)} \href{https://github.com/ksauraj/jee_counsellor}{[GitHub]}}{2023}
      \resumeItemListStart
        \resumeItem{Developed a terminal tool to help students with JEE counseling procedures.}
        \resumeItem{Parsed official data and provided personalized suggestions via terminal UX.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Telegram Bash Bot} \href{https://github.com/ksauraj/telegram-bash-bot}{[GitHub]}}{2022}
      \resumeItemListStart
        \resumeItem{Created a Telegram bot in Bash, capable of performing API-driven tasks via Telegram.}
        \resumeItem{Used as a base template for Bash-based bot development over the Telegram API.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Android Automation} \emph{(Python, GitHub API, GitLab API, Telegram API)} \href{https://github.com/autoandroida}{[GitHub]}}{2022}
      \resumeItemListStart
        \resumeItem{Built a Telegram Bot-powered service to automate Android firmware dumps, recovery creation, and repo setup.}
        \resumeItem{Streamlined Android custom ROM contributions with minimal manual input.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{K8au Shell Analyzer} \emph{(Go, TUI, AI)} \href{https://github.com/ksauraj/k8au-shell-analyzer}{[GitHub]}}{2024}
      \resumeItemListStart
        \resumeItem{Interactive terminal tool that analyzes shell command history to discover behavioral patterns.}
        \resumeItem{Used LLM-based NLP to cluster and summarize usage insights.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------SKILLS-----------
%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Go, Python, Bash, C, JavaScript, HTML/CSS, YAML, SQL} \\

    \textbf{DevOps \& Automation}{: Docker, Kubernetes, Helm, GitHub Actions, GitLab CI, Ansible, Terraform, Makefile, Docker Compose, CI/CD Pipelines, Infrastructure as Code (IaC)} \\

    \textbf{Cloud \& Platforms}{: AWS (EC2, S3, IAM, ECS, Fargate, VPC, ALB, Auto Scaling, CloudFront, CloudWatch), Azure (VNet, VMSS, Application Gateway), GCP, Oracle Cloud, Linode, Microsoft Graph API} \\

    \textbf{Observability \& Monitoring}{: Prometheus, Grafana, Loki, Promtail, Node Exporter, cAdvisor, Wazuh, Log Aggregation, Alerting} \\

    \textbf{Networking}{: TCP/IP, DNS, HTTP/HTTPS, TLS/SSL, Load Balancing, Reverse Proxies, Routing, Subnetting, VPN, API Gateways, Network Troubleshooting} \\

    \textbf{Security \& DevSecOps}{: HashiCorp Vault, SBOM Generation, Container Security, Secret Management, Vulnerability Scanning, Security Automation, PCI DSS Fundamentals, DDoS Detection, Access Control} \\

    \textbf{Databases}{: MySQL, Database Design, Query Optimization} \\

    \textbf{Linux \& Systems}{: Linux, Systemd, Shell Scripting, Tmux, Vim, Process Management, Server Administration} \\

    \textbf{Tools \& Technologies}{: Git, REST APIs, Webhooks, Kong API Gateway, Nginx, Caddy, Railway, Heroku, Cirrus CI, Android Build System, Android Firmware Development}
  }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology (B.Tech.)}{2023 -- 2027}
      {Information Technology, AKTU}{CGPA: 8.1}
  \resumeSubHeadingListEnd

\end{document}